<!--pandoc
format:html
standalone:
-->

```{r}
library(knitr)
opts_chunk$set(cache=T, tidy=F)
```

```{r}
library(ggplot2); library(plyr)
library(reshape2)
system('ghc -package ghc -O2 cabalf.hs')
system('./cabalf; mkdir generated; mv pp.csv generated')
x <- read.csv('generated/pp.csv')
xext <- ddply(x, .(ext), function(x) c(count=sum(x$count)))
nFiles <- nlevels(interaction(x$pkg, x$fileid))
```
```{r fig.cap='how many times is Extension written per file?'}
plot(ggplot(xext, aes(count / nFiles, reorder(ext, count)))
     + geom_point()
     + ylab(''))
```
Certain extensions are the most popular.

The overall frequency may not be the whole story: certain extensions tend to be enabled together. Here is a principal-components analysis. The order in which the completions are supplied matches the principal component that matches the currently enabled extensions the best. An artificial neural network (ANN) should be more appropriate?
```{r}
x2 <- ddply(x, .(pkg), function(x)
            within(count(x, c('ext'), 'count'),
                   freq <- freq/sum(freq)))
x3 <- dcast(x2, ext ~ pkg, fill=0)
x3.pcs <- princomp(t(x3[, -1]))
plot(x3.pcs)
```
```{r}
nc <- 5
comp <- paste('comp = [ [',
      do.call('paste0', list(collapse='], [',
                            lapply(1:nc, function(i)
                                   paste0(paste0('("',
                                               x3[order(x3.pcs$loadings[ , i]),1],
                                               '",',
                                               x3.pcs$loadings[, i] *
                                               x3.pcs$sdev,
                                               ')\n  '),
                                    collapse=',')))),
      ']]')

writeLines(c('module RateLang (rateLang) where
import qualified Data.Map as M
import Data.Maybe
import Data.Ord
import Data.List
rateLang :: [String] -> [String]
rateLang enabled =
  let s = zipWith (\\ cm c -> (abs $ sum $ mapMaybe (`M.lookup` cm) enabled,
                               c)) 
                comp2
                comp
  in map fst (snd (maximumBy (comparing fst) s)) \\\\ enabled
comp2 = map M.fromList comp
', comp
            ), con=file('generated/RateLang.hs'))
```
